Naming Conventions for GRSSLCM

### 2020-09-04 99-admin/naming-conventions/names.Rmd
Edit naming conventions: text clarifications

*  $P$ is used for parr (first year freshwater juveniles)
*  $M$ is used for smolt (second year freshwater juveniles)
*  $O$ is used for ocean juveniles
*  $R$ is used for returning adults
*  $S$ is used for spawning adults
*  $b$ is used to denote "before migration" 
*  $a$ is used to denote "after migration"
*  $\phi$ is used to denote a survival term, subscripts used to denote the from/to states
*  $\psi$ is used to denote maturation from ocean juvenile to returning adult (no distinction between jacks and adults because they are all sexually mature)
*  $\dot{x}$ is used to denote that $x$ is an observed quantity (data)
*  $L$ (uppercase) is used to denote that the quantity has been logit-tranformed, $l$ (lowercase) is used to denote that the quantity has been log-transformed.
*  $y$ represents brood year fish were spawned; $t$ represents return year for adults

>>>>

*  $P$ is used for parr (first year freshwater juveniles)
*  $M$ is used for smolt (second year freshwater juveniles)
*  $O$ is used for ocean juveniles
*  $R$ is used for returning adults
*  $S$ is used for spawning adults
*  $b$ is used to denote "before event", generally migration from one location to another or a mortality source 
*  $a$ is used to denote "after event"
*  $\phi$ is used to denote a survival term, subscripts used to denote the from/to states
*  $\psi$ is used to denote maturation from ocean juvenile to returning adult (no distinction between jacks and adults because they are all sexually mature)
*  $\dot{x}$ is used to denote that $x$ is an observed quantity (data)
*  $L$ (uppercase) is used to denote that the quantity has been logit-tranformed, $l$ (lowercase) is used to denote that the quantity has been log-transformed.
*  $y$ represents brood year fish were spawned for all non-adult states. For adult states, it is the brood year in which they return
